High geomagnetic field intensity recorded by anorthosite xenoliths requires a vigorous late Mesoproterozoic geodynamo

### 2022-04-06 PNAS_manuscript/Supporting Info.tex

%To check for nonlinear acqusition, we applied full TRMs to a set of anorthosite specimens with lab fields of 30, 50, 70, and 90 $\mu$T along specimen vertical axes. The results show that these anorthosite specimens did not saturate upon the applied fields and there is thus no need for correcting nonlinear thermal remanence acquisitions (\citealp{Selkin2007a}; Fig. S4).

@@

\begin{table}[]
\centering
\caption{\footnotesize{Summary paleointensity result statistics at site-level, region-level, and overall arithmetic means. The statistics names are the same as in Table \ref{tab:PINT_result}}. n represents the total number of specimen- or site- or region-level results used for calculating mean values. inc$_{tc}$ is the tilt-corrected mean inclination. Site-level means for AX6, AX8, AX10, AX11, AX12, AX13, AX16 are calculated based on specimen results. Regional means for Carlton Peak, Kennedy Creek, and Silver Bay are calculated by grouping specimen results from AX6 and AX8 and AX10, AX11 and AX13, AX12 and AX16, respectively. Overall site mean values are calculated using all site-level results in this table. Overall region-mean values are calculated using all regional mean results in this table. }
\begin{tabular}{ccccccccccc}
\hline
\multicolumn{1}{l}{}                       &               & B$_{anc}$ & n  & FRAC & GAP-MAX & MAD ($^\circ$) & DANG ($^\circ$) & inc$_{tc}$ & $\gamma$ & VDM (ZAm$^2$) \\
\hline
\multirow{7}{*}{specimen mean for sites}   & AX6           & 30.33     & 3  & 0.69 & 0.13    & 3.55           & 2.66            & 38.9       & 2.63     & 48.76         \\
                                           & AX8           & 52.4      & 3  & 0.66 & 0.17    & 4.28           & 2.15            & 40.3       & 7.3      & 83.14         \\
                                           & AX10          & 46.82     & 3  & 0.7  & 0.23    & 4.98           & 2.14            & 36.6       & 6.1      & 76.81         \\
                                           & AX12          & 38.1      & 6  & 0.75 & 0.22    & 3.26           & 2.53            & 55.2       & 5.98     & 51.31         \\
                                           & AX16          & 44.15     & 11 & 0.68 & 0.19    & 4.19           & 1.96            & 49.2       & 3.97     & 63.87         \\
                                           & AX11          & 73.34     & 7  & 0.68 & 0.19    & 3.85           & 1.82            & 35.2       & 6.63     & 121.73        \\
                                           & AX13          & 76.63     & 7  & 0.73 & 0.2     & 5.7            & 1.67            & 35.1       & 5        & 127.29        \\ 
                                           \hline
\multirow{3}{*}{specimen mean for regions} & Carlton Peak  & 43.18     & 9  & 0.68 & 0.17    & 4.27           & 2.32            & 38.6       & 5.34     & 69.57         \\
                                           & Kennedy Creek & 74.98     & 14 & 0.7  & 0.2     & 4.78           & 1.74            & 35.15      & 5.81     & 124.51        \\
                                           & Silver Bay    & 42.02     & 17 & 0.71 & 0.2     & 3.86           & 2.16            & 51.32      & 4.68     & 59.43         \\
\hline
overall site mean                          &               & 51.68     & 7  &      &         &                &                 &            &          & 81.84         \\
overall region mean                        &               & 53.39     & 3  &      &         &                &                 &            &          & 84.5         
\end{tabular}
\end{table}

>>>>

@@

\begin{table}[]
\centering
\caption{\footnotesize{Summary paleointensity result statistics at site-level, region-level, and overall arithmetic means. The statistics names are the same as in Table \ref{tab:PINT_result}}. n represents the total number of specimen- or site- or region-level results used for calculating mean values. inc$_{tc}$ is the tilt-corrected mean inclination. Site-level means for AX6, AX8, AX10, AX11, AX12, AX13, AX16 are calculated based on specimen results. Regional means for Carlton Peak, Kennedy Creek, and Silver Bay are calculated by grouping specimen results from AX6 and AX8 and AX10, AX11 and AX13, AX12 and AX16, respectively. Overall site mean values are calculated using all site-level results in this table. Overall region-mean values are calculated using all regional mean results in this table. All paleointensity values and corresponding virtual dipole moments are corrected for cooling rate by a factor of 0.75. Taking a threshold p value of 0.01, the independent two-sample t-test results show that specimen paleointensity distributions of site AX12 and AX16, and those of site AX11 and AX13 are indistinguishable; region Kennedy Creek have distinguishable distributions from the other two regions; Silver Bay region and Carlton Peak region are indistinguishable.}
\begin{tabular}{cccccccccccc}
                                           &               & B$_{anc}$ & n  & FRAC & GAP-MAX & MAD ($^\circ$) & DANG ($^\circ$) & inc$_{tc}$ & Paleolatitude & $\gamma$ & VDM (ZAm$^2$) \\ \hline
\multirow{7}{*}{specimen mean for sites}   & AX6           & 22.8      & 3  & 0.69 & 0.13    & 3.6            & 2.7             & 38.9       & 22.0          & 2.6      & 49.5          \\
                                           & AX8           & 39.4      & 3  & 0.66 & 0.17    & 4.3            & 2.2             & 40.3       & 23.0          & 7.3      & 84.4          \\
                                           & AX10          & 35.2      & 3  & 0.70 & 0.23    & 5.0            & 2.1             & 36.6       & 20.4          & 6.1      & 77.9          \\
                                           & AX11          & 55.2      & 7  & 0.68 & 0.19    & 3.8            & 1.8             & 35.2       & 19.4          & 6.6      & 123.6         \\
                                           & AX12          & 28.6      & 6  & 0.75 & 0.22    & 3.3            & 2.5             & 55.2       & 35.7          & 6.0      & 52.1          \\
                                           & AX13          & 57.6      & 7  & 0.73 & 0.2     & 5.7            & 1.7             & 35.1       & 19.4          & 5.0      & 129.2         \\
                                           & AX16          & 33.2      & 11 & 0.68 & 0.19    & 4.2            & 2.0             & 49.2       & 30.1          & 4.0      & 64.8          \\ \hline
\multirow{3}{*}{specimen mean for regions} & Carlton Peak  & 32.5      & 9  & 0.68 & 0.17    & 4.3            & 2.3             & 38.6       & 21.8          & 5.3      & 70.6          \\
                                           & Kennedy Creek & 56.4      & 14 & 0.70 & 0.20    & 4.8            & 1.7             & 35.2       & 19.4          & 5.8      & 126.4         \\
                                           & Silver Bay    & 31.6      & 17 & 0.71 & 0.20    & 3.9            & 2.2             & 51.3       & 32.1          & 4.7      & 60.3          \\ \hline
overall site mean                          &               & 38.9      & 7  &      &         &                &                 &            &               &          & 83.1          \\
overall region mean                        &               & 40.2      & 3  &      &         &                &                 &            &               &          & 85.8         
\end{tabular}
\end{table}
